Precise spiking motifs in neurobiological and neuromorphic data

### 2022-10-18 manuscript.tex
Update on Overleaf.
Update manuscript.tex

\section{Precisely timing motifs in computational neuroscience}

@@

\subsection{Extending the decoding at multiple time scales}

@@

\begin{figure}
\centering
%\includegraphics{https://www.pnas.org/cms/10.1073/pnas.1718518116/asset/ab9a48f6-b28f-40c1-978e-6f6dbec39b98/assets/graphic/pnas.1718518116fig01.jpeg}
\caption{Mixed distance and duration representation in CA1. (A) Calcium fluorescence (heatmap) of CA1 neurons participating to run sequences in consecutive imaging sessions. Cells have been selected and ordered with respect to their activity in the first imaging session (Top). The black line represents speed of the mouse.}\label{fig:haimerl}
\end{figure}

>>>>

\section{Precisely-timed spiking motifs in computational neuroscience}

@@

https://www.overleaf.com/project/633bf90497b5b325a3ff692e
\subsection{Extending the decoding athttps://www.overleaf.com/project/633bf90497b5b325a3ff692e multiple time scales}

@@

% Currently, few interdisciplinary research projects take full advantage of event-based representations in computational and biological neuroscience. Nevertheless, there is a substantial literature in neurobiology indicating that brain dynamics often organize into stereotyped sequences (like synfire chains (Ikegaya et al., 2004), packets (Luczak et al., 2007) or hippocampal sequences (Pastalkova et al., 2008; Villette et al., 2015)  and on the role of such precise spike timing in downstream information transfer and coding (Branco et al., 2010; Buzsáki & Tingley, 2018; Luczak et al., 2015). In particular, one theoretical viewpoint considers synfire braids (Bienenstock, 1995), where a precise sequential motif of spikes will synchronize as it reaches the soma of a neuron for which synaptic delays are adequately tuned. In particular, computational modeling shows that at the scale of neurons, an efficient neural code can emerge where spike times are organized in prototypical, precise temporal motifs (Izhikevich, 2006) which he defined as polychronous groups.

%Stereotyped sequences of neuronal activation have been particularly well described in the adult hippocampus and related to its function in mental travel in time and space (Buzsáki & Tingley, 2018). These sequences can be internally generated (Pastalkova et al., 2008; Villette et al., 2015) and are formed by the chained activation of orthogonal assemblies, themselves organized as sequence packets (Malvache et al., 2016). Thus, hippocampal sequences are formed by the ordered activation of smaller sequence motifs. They are stereotyped and robust, since neurons can be activated in the same order across days (see Figure 2 of (Haimerl et al., 2019)). As a consequence, hippocampal sequences may rely on an internally hardwired structure and form the functional building blocks for encoding, storing and retrieving experience.  
\begin{figure}
\centering
\includegraphics{figures/haimerl2019.jpg}
\caption{
%  Figure 2: An example of a polychronous group seen in cortical slices. In this study by (Haimerl et al., 2019), an analysis of the raster plot shows repetitions of precise spiking motifs with a time scale of the order of seconds.  
Mixed distance and duration representation in CA1. (A) Calcium fluorescence (heatmap) of CA1 neurons participating to run sequences in consecutive imaging sessions. Cells have been selected and ordered with respect to their activity in the first imaging session (Top). The black line represents speed of the mouse.}\label{fig:haimerl}
\end{figure}
